### 2019-01-06 Sections/a_new_frontier_towards_the_singularity.tex
just doing a save
essays and references
Edited NISQ and QKD essays
Ecosystems stub
Added authors to sections
+quotes, formatting

\dropcap{I}{n} this part we provide a non-technical outlook on the future quantum internet and its implications, for the benefit of the technically disinterested reader, who merely wishes to grasp some of the `big issues'. This section is in the form of several short essays, requiring no technical background knowledge in quantum computation, quantum mechanics, or mathematics.

We acknowledge that while parts of these essays are highly plausible, if not certain, others are highly speculative, but nonetheless based on believable although somewhat futuristic reasoning. At the very least we hope to stimulate the exchange of ideas and their development. We encourage the reader to question the ideas presented in these essays and put forth their own ideas and predictions.

\famousquote{There is no harm in doubt and skepticism, for it is through these that new discoveries are made.}{Richard Feynman}

@@

\latinquote{Deus ex Machina.}

@@

>>>>

\famousquote{Only the very weak-minded refuse to be influenced by literature and poetry.}{Cassandra Clare}
\newline

\famousquote{There is no harm in doubt and skepticism, for it is through these that new discoveries are made.}{Richard Feynman}
\newline

\dropcap{I}{n} this part we provide a non-technical outlook on the future quantum internet and its implications, for the benefit of the technically disinterested reader, who merely wishes to grasp some of the `big issues'. This section is in the form of a collection of short essays, requiring little or no technical background knowledge in quantum computation, quantum mechanics, or mathematics.

We acknowledge that while parts of these essays are certainly highly plausible, if not certain, others are highly speculative, but nonetheless based on believable although somewhat futuristic (perhaps even bordering science fiction) reasoning. We can't predict the future. But at the very least we hope to stimulate the exchange of ideas, and promote their exploration and development. After all, the great ideas of the future always begin speculatively! We encourage the reader to critically question the ideas presented in these essays, and put forth their own thoughts and predictions for what the quantum future may bring and the implications it will have for humanity.

@@

\latinquote{Deus ex machina.}

@@

%
% NISQ
%

\input{Sections/essay_NISQ_QC}

%
% Future of QKD
%

\input{Sections/essay_to_the_future_QKD}

% 
% Quantum Ecosystem
%

\input{Sections/essays_quantum_ecosystem}

\latinquote{Disiecti membra poetae.}

### 2019-01-06 Sections/acknowledgements.tex

\begin{itemize}
\item We acknowledge Gavin Brennen, Chris Ferrie, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Ryan Mann, Jonathan Olson, Samuel Marks \& Alexis Shaw for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item Peter P. Rohde is funded by an Australian Research Council Future Fellowship (project FT160100397).
\item Tim Byrnes is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item Jonathan P. Dowling would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{1,3,7-Trimethylxanthine}\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

>>>>

\begin{itemize}
\item We acknowledge Gavin Brennen, Chris Ferrie, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Ryan Mann, Jonathan Olson, Samuel Marks, Nicholas Umashev, Elija Perrier, Kate Hrayssi \& Alexis Shaw for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item Peter P. Rohde is funded by an Australian Research Council Future Fellowship (project FT160100397).
\item Tim Byrnes is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item Jonathan P. Dowling would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{1,3,7-Trimethylxanthine}\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

### 2019-01-06 Sections/classical_networking_protocols.tex
Finished indexing hierarchy
Fixed up fig sizes for 1 col
indexing
Added authors to sections

@@

\dropcap{T}{here} have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet!Switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency-multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collisions!Detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsection{Gateway protocols \& routing tables} \label{sec:gateway} \index{Gateway protocols} \index{Routing tables}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{network_hierarchy}
	\captionspacefig \caption{Simple example of a network with two levels in its hierarchy. At the lowest level are 4 different subnets belonging to different departments within an organisation, each of which implements Ethernet networking. Above this, the subnets connect together in a star network via a central router. By subdividing the network hierarchy as such, if most traffic emanating within a subnet stays within that same subnet, collisions between packets on different subnets are avoided, thereby improving the efficiency of the subnets' Ethernet implementations.} \label{fig:net_hierarchy}
\end{figure}

>>>>

\sectionby{Darryl Veitch \& Peter Rohde}

\famousquote{Mobile phones should be left to the kids. They're the only ones who can operate them.}{Anthony Hincks}
\newline

@@

\dropcap{T}{here} have been numerous approaches employed in the past for sharing communications links between multiple users\index{Shared communication channels}. This includes:
\begin{itemize}
	\item Channel-switching: an entire communications channel is designated for exclusive use by a given user. \index{Channel-switched networks}
	\item Packet-switching: data is divided into packets, which are routed independently by the network, being reconstructed by the recipient once all packets have been received.\index{Packet!Switching}
	\item Time- or frequency-multiplexing: each user is designated a particular frequency spectrum or series of time-slots exclusively for their use. \index{Time-multiplexing}\index{Frequency!Multiplexing}
	\item Code Division Multiple Access (CDMA): all users can broadcast over a channel simultaneously, and the construction of the coding technique enables demultiplexing of the distinct signals, despite their interference with one another.\index{Code Division Multiple Access (CDMA)}
	\item Ethernet: all users are free to broadcast\index{Broadcast networks} over a shared channel at will, and \textit{collision detection}\index{Collisions!Detection} identifies when packets interfere, after which they are discarded and rebroadcast following a random waiting period, repeating until success.\index{Ethernet}
\end{itemize}

@@

\subsection{Gateway protocols \& routing tables} \label{sec:gateway} \index{Gateway protocols} \index{Routing!Tables}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{network_hierarchy}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{network_hierarchy}
\fi
	\captionspacefig \caption{Simple example of a network with two levels in its hierarchy. At the lowest level are 4 different subnets belonging to different departments within an organisation, each of which implements Ethernet networking. Above this, the subnets connect together in a star network via a central router. By subdividing the network hierarchy as such, if most traffic emanating within a subnet stays within that same subnet, collisions between packets on different subnets are avoided, thereby improving the efficiency of the subnets' Ethernet implementations.} \label{fig:net_hierarchy}
\end{figure}

### 2019-01-06 Sections/economics_of_the_quantum_internet.tex

Thus, we can reasonably anticipate that the quantum internet will not evolve like the classical `internet of things'\index{Internet of things}, whereby a massive number of ultra-small computational resources are scattered across the globe and networked. Rather, a relatively small number of central `hubs'\index{Hubs} are likely to emerge, which centralise enormous computational power, interconnected via the quantum internet to form the globally unified quantum cloud (Sec.~\ref{sec:glob_unif_quant_cloud}).

Much like the classical internet, it's to be expected the network that will emerge will approximate a scale-free network (Sec.~\ref{sec:scale_free_networks})\index{Scale-free networks}, with a very hierarchical structure, following a Pareto distribution\index{Power!Law} in hub-size.

@@

>>>>

Thus, we can reasonably anticipate that the quantum internet will not evolve like the classical `internet of things' (IoT)\index{Internet of things (IoT)}, whereby a massive number of ultra-small computational resources are scattered across the globe and networked. Rather, a relatively small number of central `hubs'\index{Hubs} are likely to emerge, which centralise enormous computational power, interconnected via the quantum internet to form the globally unified quantum cloud (Sec.~\ref{sec:glob_unif_quant_cloud}).

Much like the classical internet, it's to be expected the network that will emerge will exhibit a very hierarchical structure, following a Pareto distribution\index{Power!Law} in hub-size.

@@

\famousquote{People are always selling the idea that people with mental illness are suffering. I think madness can be an escape. If things are not so good, you maybe want to imagine something better.}{John Nash}
\newline

### 2019-01-06 Sections/essay_quantcoin.tex

>>>>

\famousquote{Bitcoin is the most stellar and most useful system of mutual trust ever devised.}{Santosh Kalwar}
\newline

\famousquote{By 2030, some form of Crypto will become the global reserve currency but it will not be based on what exists today. Existing cryptos need to transform or will disappear. Also around 2030 or so, the first Nobel Prize in Economics will be awarded to a Cryptoeconomist.}{Tom Golway}
\newline

### 2019-01-06 Sections/essay_the_economics_of_the_quantum_internet.tex

@@

The future quantum economy might be made more efficient by artificially transferring capital from low-multiplier sectors to high-multiplier quantum technologies. Or maybe the market will do this on its own accord\footnote{Have faith in the invisible hand.}? This is a uniquely quantum consideration that never previously applied to conventional supercomputing\index{Supercomputers}. The onset of the quantum era may redefine our entire economic mindset and fiscal policy-making, to adapt to the unique economic idiosyncrasies of this emerging technology.

>>>>

\famousquote{Underlying most arguments against the free market is a lack of belief in freedom itself.}{Milton Friedman}
\newline

@@

The future quantum economy might be made more efficient by artificially transferring capital from low-multiplier sectors to high-multiplier quantum technologies. Or maybe the market will do this on its own accord\footnote{Have faith in the invisible hand.\index{Adam Smith}}? This is a uniquely quantum consideration that never previously applied to conventional supercomputing\index{Supercomputers}. The onset of the quantum era may redefine our entire economic mindset and fiscal policy-making, to adapt to the unique economic idiosyncrasies of this emerging technology.

### 2019-01-06 Sections/protocols_for_the_quantum_internet.tex

For cryptographic purposes , there are far more stringent constraints placed upon our random number generator than for use in say a Monte-Carlo computer simulation -- cryptographic random number generation\index{Cryptographic!Random number generation}. In this context, the demands placed upon the amount of bias or correlations in the random number stream are very stringent. An enormous amount of research has been invested into this topic, and sophisticated statistical tests have been developed for establishing crypto-worthiness of a random number stream. The fact that quantum random numbers, via the inherent non-determinism of quantum mechanics, do not obey any hidden variable theory, implies there is intrinsically no underlying `seed'\index{Random!Seed} to the random number stream, which reveals the entire deterministic sequence. This is unlike any classical generator, where there always is such a seed, but it is simply taken to be too hard to determine.

@@

\subsection{Open-destination quantum state teleportation}\index{Open-destination quantum state teleportation}\label{sec:open_dest_q	st}

@@

Next, note that performing an $\hat{X}$-basis measurement on one qubit in a GHZ state reduces it to an \mbox{$n-1$}-qubit GHZ state, up to a potential local $\hat{Z}$-correction,
\begin{align}
	\braket{+|\psi_\mathrm{GHZ}^{(n)}} &= \ket{\psi_\mathrm{GHZ}^{(n-1)}},\nonumber\\
	\braket{-|\psi_\mathrm{GHZ}^{(n)}} &= \hat{Z}\ket{\psi_\mathrm{GHZ}^{(n-1)}}.
\end{align}
Performing this contraction repeatedly ultimately reduces us all the way down to a single Bell pair.

>>>>

For cryptographic purposes, there are far more stringent constraints placed upon our random number generator than for use in say a Monte-Carlo computer simulation -- cryptographic random number generation\index{Cryptographic!Random number generation}. In this context, the demands placed upon the amount of bias or correlations in the random number stream are very stringent. An enormous amount of research has been invested into this topic, and sophisticated statistical tests have been developed for establishing crypto-worthiness of a random number stream. The fact that quantum random numbers, via the inherent non-determinism of quantum mechanics, do not obey any hidden variable theory, implies there is intrinsically no underlying `seed'\index{Random!Seed} to the random number stream, which reveals the entire deterministic sequence. This is unlike any classical generator, where there always is such a seed, but it is simply taken to be too hard to determine.

@@

\subsection{Open-destination quantum state teleportation}\index{Open-destination quantum state teleportation}\label{sec:open_dest_qst}

@@

Next, note that performing an $\hat{X}$-basis measurement on one qubit in a GHZ state reduces it to an \mbox{$n-1$}-qubit GHZ state, up to a potential local $\hat{Z}$-correction,
\begin{align}
	\braket{+|\psi_\mathrm{GHZ}^{(n)}} &= \ket{\psi_\mathrm{GHZ}^{(n-1)}},\nonumber\\
	\braket{-|\psi_\mathrm{GHZ}^{(n)}} &= \hat{Z}\ket{\psi_\mathrm{GHZ}^{(n-1)}}.
\end{align}
Performing this contraction repeatedly ultimately reduces us all the way down to a single Bell pair, since,
\begin{align}
	\ket{\psi_\mathrm{GHZ}^{(2)}} = \ket{\Phi^+}.
\end{align}
